\section{Conclusion}

This project has introduced some great learning experiences, together with a decent amount of challenges along the way. The first step was learning about all the different software technologies, both the ones introduced in the course, and the additional ones that were included in the application like Firebase and H2 database. The biggest challenge might have been understanding how relations between entities worked in a relational database, and how to configure them in a proper way. These entity classes also had to be integrated with the Spring application. This made the learning curve relatively steep for the earlier parts of the project. Luckily, the Spring framework documentation covers a vast variety of topics, and there are a multitude of guides on how to integrate different technologies with Spring.

This made the learning curve flatten a bit after getting a decent understanding of each of the technologies. However, even with associated guides, not every technology behaved as expected when trying to implement them. Originally, the project was supposed to use MongoDB \cite{mongodb} as the non-relational database. Implementing MongoDB with the H2 database turned out to give some unexpected errors, and after a few days of trial and only getting errors it was decided to use Firebase as the non-relational database instead. This was fortunately the only major speedbump that the project hit. Implementing the messaging system with RabbitMQ and Dweet.io was for the most part unproblematic, using the respective technologies own documentation for understanding their core concepts and how to utilize them properly. 

The reference list includes a set of online sites used throughout the project when learning about the different technologies and examples of how to implement them into other projects. Most of the references listed are for the software technologies not introduced in the course.

